### 2012-09-13 docs/architecture/architecture.tex

To access the data, we loop over all the levels, and all the boxes in
the given level.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    do n=1,nlevs
       do i = 1, nboxes(s(n))
\end{lstlisting}
{\tt nboxes(s(n))} is simply the number of boxes in level {\tt n}.
All data in all \multifab s will have the same box layout, so we only
need to query the number of boxes from one \multifab.

For a given \boxtype, we get the data and the bounds of the \boxtype.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
          if ( multifab_remote(s(n), i) ) cycle
          sp  => dataptr(s(n), i)
          ump => dataptr(umac(n,1),i)
          vmp => dataptr(umac(n,2),i)
          lo =  lwb(get_box(s(n), i))
          hi =  upb(get_box(s(n), i))
\end{lstlisting}

\noindent For parallel runs, there is no guarantee that the particular
box is on the current processor.  The function {\tt multifab\_remote}
returns {\tt .true.} if the box is off-processor, in which case, we 
simply skip to the next box.

>>>>

To access the data, we loop over all the levels, and all the boxes in
the given level.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    do n=1,nlevs
       do i = 1, nfabs(s(n))
\end{lstlisting}
{\tt nfabs(s(n))} is simply the number of boxes in level {\tt n} on
the current processor.  Each processor knows which \fab s in its
\multifab are local to that processor, and this loop will only loop
over those.

For a given \boxtype, we get the data and the bounds of the \boxtype.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
          sp  => dataptr(s(n), i)
          ump => dataptr(umac(n,1),i)
          vmp => dataptr(umac(n,2),i)
          lo =  lwb(get_box(s(n), i))
          hi =  upb(get_box(s(n), i))
\end{lstlisting}
